Distributions

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Progress with figures.

ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
  #           color = "blue") +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")
```

@@

# Figure 2 - 
HERE - get rid of the first panel. Make figure later with percent support at the pooling levels so Fig 2 only shows the importance of variaiton since different models fit different bootsptraps.

```{r fig.width=12}

cp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, boot) %>%
  group_by(boot) %>%
  distinct() %>%
  ungroup() %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  mutate(model = "CP") %>%
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  geom_col() +
  labs(y = "Percent Support") +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>% filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2) -> cp.fit

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
  group_by(fgroup, boot) %>%
  distinct() %>%
  group_by(fgroup) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2) -> pp.fit

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2)  -> np.fit

legend <- get_legend(np.fit + theme(legend.position = "bottom") +
                       guides(fill=guide_legend(title="Distribution")))

plot_grid(cp.fit, pp.fit, 
          np.fit + theme(legend.position = "none"), 
          ncol = 3, rel_widths = c(0.8,1,1.4)) -> col_grid

plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))

@@

```
# Figure 3

```{r}
cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, color = dist, y = BIC)) +
  geom_boxplot() +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Pooling Model", y = "Raw BIC values") +
  theme_classic()
```

```{r}
cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2) +
  geom_col() +
  theme_classic() +
  labs(x = "Pooling Level", y = "Percent Support")
```

# Table 1 -

@@

@@

Fix this. The idea is that each bootstrap is represented here with their BIC value for each model. We see that there's very strong evidence for the multi distribution model at both PP and NP levels. The summary quantiles later show extre support for this.

```{r}
plot_grid(cp.bic %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  geom_point(),
  pp.bic %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  geom_point(),
  np.bic %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  geom_point(), nrow = 3)

@@

>>>>

ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = id), color = "grey", 
            stat = "density", alpha = 0.8) +
  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
  #           color = "blue") +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")
```

@@

@@

```
# Table 1 -

@@

# Figure 2 -

```{r fig.width=12, fig.height=6}

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist)) -> pooling.support

# cp.boot.fits %>%
#   dplyr::select(., bic, dist, dBIC, boot) %>%
#   group_by(boot) %>%
#   distinct() %>%
#   ungroup() %>%
#   filter(dBIC == 0) %>%
#   count(dist) %>%
#   mutate(prcnt_support = n/nboots) %>%
#   mutate(model = "CP") %>%
#   ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
#   geom_col() +
#   labs(y = "Percent Support") +
#   theme_classic() +
#   theme(legend.position = "none",
#         axis.title.x = element_blank()) +
#   geom_label(data = bestmodel %>% filter(., model == "CP"),
#              aes(x = model, y = -0.05, label = dist)) +
#   scale_fill_manual(values = cols.fig2) -> cp.fit

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
  group_by(fgroup, boot) %>%
  distinct() %>%
  group_by(fgroup) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2) -> pp.support

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2)  -> np.support

# legend <- get_legend(np.fit + theme(legend.position = "bottom") +
#                        guides(fill=guide_legend(title="Distribution")))
model.legend <- get_legend(pooling.support + theme(legend.position = "bottom") +
                             guides(fill=guide_legend(title = "Distribution model")))

# plot_grid(cp.fit, pp.fit, 
#           np.fit + theme(legend.position = "none"), 
#           ncol = 3, rel_widths = c(0.8,1,1.4)) -> col_grid
# 
# plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))

# first_row <- plot_grid(NULL, 
#                        pooling.support + theme(legend.position = "none"),
#                        NULL, rel_widths = c(0.3, 1, 0.3))
# 
# second_row <- plot_grid(pp.support, 
#                         np.support + theme(legend.position = "none"),
#                         ncol = 2, rel_widths = c(1, 1.2))
# plot_grid(pooling.support + theme(legend.position = "none"),
#           second_row, model.legend, nrow = 3, rel_heights = c(1,1,0.2))

bar_col <- plot_grid(pooling.support + theme(legend.position = "none"),
                     pp.support, 
                     np.support + theme(legend.position = "none"),
                     ncol = 3, rel_widths = c(0.4, 1, 1.4))
plot_grid(bar_col, model.legend, nrow = 2, rel_heights = c(1, 0.1))

# Figure 3

```{r}
cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, color = dist, y = BIC)) +
  geom_boxplot() +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Pooling Model", y = "Raw BIC values") +
  theme_classic() +
  guides(color=guide_legend(title = "Distribution model")) +
  theme(legend.position = "bottom")

@@

Fix this. The idea is that each bootstrap is represented here with their BIC value for each model. We see that there's very strong evidence for the multi distribution model at both PP and NP levels. The summary quantiles later show very high support for this. Difference here between incorporating variation at the expense of sample size, and getting high support, or staying with high sample size without variation.

```{r fig.height=6}

cp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "") +
  theme(legend.position = "none") -> Fig4a

pp.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "") +
  theme(legend.position = "none") -> Fig4b

np.bic %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  #geom_col() +
  geom_point() +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") -> Fig4c

legend4 <- get_legend(Fig4c +
                       guides(color=guide_legend(title = "Distribution \n model")))

plot_grid(Fig4a, Fig4b, 
          Fig4c + theme(legend.position = "none"), nrow = 3) -> fig4

plot_grid(fig4, legend4, ncol = 2, rel_widths = c(1, 0.15))

@@

What about the parameters of the best fit distributions? Meaning, that for each boostrap, keep only the best model. Plot those.

```{r fig.height=6}
cp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

**PP**

```{r fig.height=6}
pp.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate, x = fgroup)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

**NP**

```{r fig.height=6}
np.boot.fits %>% 
  filter(., dBIC == 0) %>% 
  ggplot(., aes(y = estimate, x = individual)) +
  facet_wrap(dist~param, ncol = 2, scales = "free") +
  geom_boxplot()
```

# Visualize them as density curves:
